Topological Equivariance Artist Model

### 2021-03-12 paper/paper.tex
gonna delete all this but whatever

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
\keywords{Taxonomy, Models, Frameworks, Theory }

%% ACM Computing Classification System (CCS). 
%% See <http://www.acm.org/class/1998/> for details.
%% The ``\CCScat'' command takes four arguments.

\CCScatlist{ % not used in journal version
 \CCScat{K.6.1}{Management of Computing and Information Systems}%
{Project and People Management}{Life Cycle};
 \CCScat{K.7.m}{The Computing Profession}{Miscellaneous}{Ethics}
}

@@

%% the only exception to this rule is the \firstsection command
\firstsection{Introduction}
\maketitle
The aim of this work is to rearchitecture Matplotlib to take advantage of developments in software design, data structures, and visualization, 
to improve consistency, reusability, and discoverability, so that domain specific tool developers can build structure preserving visualization tools. We present a visualization model that formalizes constraints on componenents of a visualization in terms of equivaraiance, continuity, and composibility.

\section{Background}
\begin{figure}[tb]
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
  \includegraphics[width=\columnwidth]{paper-count-w-2015-new}
  \caption{A visualization of the 1990--2015 data from \autoref{tab:vis_papers}. The image is from \cite{Isenberg:2017:VMC} and is in the public domain.}
  \label{fig:sample}
 \end{figure}

@@

\bibliography{template}
\end{document}

>>>>

%% Keywords that describe your work. Will show as 'Index Terms' in journal
%% please capitalize first letter and insert punctuation after last keyword
% http://ieeevis.org/year/2021/info/call-participation/paper-keywords
\keywords{Taxonomy, Models, Frameworks, Theory }

%% ACM Computing Classification System (CCS). 
%% See <http://www.acm.org/class/1998/> for details.
%% The ``\CCScat'' command takes four arguments.
%https://www.acm.org/publications/computing-classification-system/1998/top
\CCScatlist{ % not used in journal version
 \CCScat{I.3.6}{Computer Graphics}%
{Methodology and Techniques}{Graphics data structures and data types};}

@@

%% the only exception to this rule is the \firstsection command
\firstsection{Introduction}
\maketitle
The work presented in this paper is motivated by a need for a library of visualization components that developers could use to build complex, domain specific tools tuned to the semantics and structure carried in domain specific data. While many researchers have identified and described important aspects of visualization, they have specialized in such different ways as to not provide a model general enough to natively support the full range of data and visualization types many general purpose modern visualization tools may need to support. The core architecture also needs to be robust to the big data needs of many visualization practitioners, and therefore support distributed and streaming data needs. To support both exploratory and confirmatory visualization\cite{tukeyWeNeedBoth1980}, this tool needs to support 2D and 3D, static, dynamic and interactive visualizations.

Specifically, this work was driven by a rearchitecture of the Python visualization library Matplotlib\cite{hunterMatplotlib2DGraphics2007} to meet modern data visualization needs. We aim to take advantage of developments in software design, data structures, and visualization to improve the consistency, composibility, and discoverability of the API. We take a functional approach because functional paradigms encourage writing APIs that are flexible, concise and predictable due to the lack of side effects \cite{loudenProgrammingLanguagesPrinciples2010}. Furthermore, by structuring the API in terms of composition of the smallest units of transformation for which we can define correctness, a functional paradigm naturally leads to a library of highly modular components that are composable in such a way that by definition the composition is also correct. This allows us to ensure that domain specific visualizations built on top of these components are also correct without needing knowledge of the domain.

In this work, we present a framework for understanding visualization as equivariant maps between topological spaces. Using this mathematical formalism, we can interpret and extend prior work and also develop new tools. We validate our model by using it to re-design artist and data access layer of Matplotlib, a general purpose visualization tool.

\section{Background}
\begin{figure}[tb]
  \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
  \includegraphics[width=\columnwidth]{}
  \label{fig:sample}
 \end{figure}

@@

\bibliography{../draft/glasslab_viz.bib}
\end{document}
